Checkpoint 3

### 2020-04-23 Checkpoint3.Rmd
update table

+------------------------+---------------------------------------------------+
| Variables:             | Meaning:                                          |
+========================+===================================================+
| `polyname`             | State Name                                        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `StateColor`           | Political Leaning                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_hispanic`      | Percent of the Population that is Hispanic        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_white`        | Percent of the Population that is White           |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_asian`        | Percent of the Population that is Asian           |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_black`        | Percent of Population that is Black               |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`total_population`      | Total State Population                            | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`per_capita_income`     | Income per Capita                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `Winner`               | Indicator for whether a Republican or Democrat Won| 
|                        |                                                   |  
+------------------------+---------------------------------------------------+
|`total_2016`            | Total Number of Votes                             | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+

>>>>

+------------------------+---------------------------------------------------+
| Variables:             | Description:                                      |
+========================+===================================================+
| `polyname`             | State Name                                        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `StateColor`           | Political Leaning                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_hispanic`      | Percent of the Population that is Hispanic        |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_white`        | Percent of the Population that is White           |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_asian`        | Percent of the Population that is Asian           |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `percent_black`        | Percent of Population that is Black               |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`total_population`      | Total State Population                            | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`per_capita_income`     | Income per Capita                                 |
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_democrat2016`  | Percent of votes won by Democrat (Clinton)        |  
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`percent_republican2016`| Percent of votes won by Republican (Trump)        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
| `Winner`               | Indicator for whether a Republican or Democrat Won| 
|                        |                                                   |  
+------------------------+---------------------------------------------------+
|`total_2016`            | Total Number of Votes                             | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`Positive`              | Number of reported positive COVID-19 cases        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`Negative`              | Number of reported negative COVID-19 cases        | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`date`                  | Date of report                                    | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`death`                 | Total Number of reported deaths due to COVID-19   | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`hospitalized`          | Total Number of indivudals hopitalized due        |
|                        | to COVID-19                                       |
+------------------------+---------------------------------------------------+
|`totalTestResults`      | Total Number test results (Positive +Negative)    | 
|                        |                                                   | 
+------------------------+---------------------------------------------------+
|`FIPS`                  | A five-digit Federal Information Processing       |
|                        | Standards code which uniquely identified counties |
|                        | and county                                        | 
+------------------------+---------------------------------------------------+
